Dark matter halo shapes in the Auriga simulations

### 2019-08-21 Document/paper.tex
update

The second part of our findings correspond to the disc-halo alignment.
The dominant trend is that of a strong alignment between
the disc and the dark matter halo shape at all radii. 
In six halos of our sample we find a chaning alignment as a function
of radius.
This implies a twisting in the halo shape as a function of
radius.

Twisting has been also reported as an uncommon feature in some 
simulated systems found in the literature. 
\cite{JingSuto02} reported a shell alignment twisting in their dark
matter only simulations as measured in the direction changes of large
and medium shape axis. 
They only had three high resolution MW-like halos (with
$\sim 10^{6}$ inside the virial radius) and could not make a
statistical statement about the impact of this effect.
However, they see the twisting as an artifact resulting from high
values  of the $b/a$ ratios that make the determination of the medium
axis noisy, an effect that we have demonstrated can be discarded for
our simulations.
\cite{Bailin05} used seven hydrodynamic simulations to study the disc
halo alignment as a function of radius.
For radii smaller than $0.1R_{200}$ they find a strong global
alignment between the halo and the disc.
However, in some halos, at larger radii the angle between the
components twists resulting in a weaker correlation between the disk
and the halo shape. 
Considering that twisting is not present in our DMO simulations, it is
very likely that the detailed radial dependence of the alignments
between the disc and the halo depends on the hydrodynamics and
feedback implementations.

@@

Using dark matter only simulations, \citet{VeraCiro11} suggested that
the current dark matter halo shape strongly correlates with the time
evolution of the halo as traced by the shape measured at the virial radius. 
This effect might largely be washed out and no longer hold once baryons are included. 
The opposite trend of triaxiality in MHD simulation as a function of
radius compared to the DMO simulations, together with the twisting effect in some of 
the halos, seems to suggest that memory of the historical buildup is at most poorly 
reflected in the shapes of baryonic halo at $z=0$.

>>>>

The second part of our findings correspond to the disc-halo alignment.
The dominant trend is that of a strong alignment between
the disc and the dark matter halo shape at all radii. 
In six halos of our sample we find a chaning alignment as a function
of radius.
This implies a twisting in the halo shape as a function of
radius.
Considering that this effect is not present in our DMO simulations, it is
very likely that the detailed radial dependence of the alignments
between the disc and the halo depends on the hydrodynamics and
feedback implementations.

Twisting has been also reported as an uncommon feature in some 
simulated systems found in the literature. 
\cite{JingSuto02} reported it in their dark
matter only simulations as measured in the direction changes of large
and medium shape axis. 
They only had three high resolution MW-like halos and could not make a
statistical statement about the significance of this effect.
However, they see the twisting as an artifact resulting from high
values  of the $b/a$ ratios that make the determination of the medium
axis noisy, an effect that we have demonstrated can be discarded for
our simulations.
\cite{Bailin05} used seven hydrodynamic simulations to study the disc
halo alignment as a function of radius.
For radii smaller than $0.1R_{200}$ they find a strong global
alignment between the halo and the disc.
However, in some halos, at larger radii the angle between the
components twists resulting in a weaker correlation between the disk
and the halo shape. 
A more recent study by \cite{2015MNRAS.453..721V} used the EAGLE simulations to
report the median alignment between the stellar and dark matter
components in $1008$ galaxies around the MW mass range. 
Our results agree on the high degree of alignment on average as a
function of radius.
However, the authors do not mention whether they find any outliers
with the kind of twisting we report here.

@@

Using dark matter only simulations, \citet{VeraCiro11} suggested that
the current dark matter halo shape strongly correlates with the time
evolution of the halo as traced by the shape measured at the virial radius. 
This effect might largely be washed out and no longer hold once baryons are included. 
The opposite trend of triaxiality in MHD simulation as a function of
radius compared to the DMO simulations, together with the twisting effect in some of 
the halos, seems to suggest that memory of the historical buildup is at most poorly 
reflected in the shapes at $z=0$.
